Shifting mutational effects on the evolutionary landscape of HIV Envelope

### 2017-11-18 paper/manuscript.tex
added diff prefs logoplot
joy plots of pref-to-pref differences

>>>>

\begin{figure}
\begin{fullwidth}
{\bf \Large A} \hspace{0.61\textwidth} {\bf \Large B} \\
\hspace{0.01\textwidth} 
\includegraphics[width=0.58\textwidth]{figures/prefs_distance/prefs_distance.pdf}
\hspace{0.03\textwidth}
\includegraphics[clip=true, trim=0in 0in 0in 1.2in, width=0.68\textwidth]{figures/distance_distribution.pdf}
\vspace{0.15in}
\\ 
{\bf \Large C} \\
\includegraphics[width=1.3\textwidth]{figures/shifted_sites.pdf}
\caption{\label{fig:diffprefs}
Difference in preferences.
}
\figdata{The corrected distances between BG505 and BF520 at each site are in \texttt{BG505\_to\_BF520\_prefs\_dist.csv}.}
\end{fullwidth}
\end{figure}
\FloatBarrier
